MsCcHSFeed Outline

### 2022-11-01 MsCcHSFeedOutlineDec15.Rmd
Added sample sizes to figure 3

```{r}
data$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
datadead$fate <- factor(datadead$fate, levels = c("dead", "wander", "em", "wowe", "wowe mongo"))
```

@@

```{r}
barsdead <- ggplot(data = datadead, aes(x = treatment, fill = fate)) + 
  theme_bw() + 
  geom_bar(position = "fill") + 
  facet_wrap(~food) + 
  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
  scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
                    labels = c("Died", "Wander", "WE", "Small WOWE", "Large WOWE"))

>>>>

```{r}
datadead$treatment <- factor(data$treatment, levels = c("NP NHS", "NP HS", "P NHS", "P HS"))
datadead$fate <- factor(datadead$fate, levels = c("dead", "wander", "em", "wowe", "wowe mongo"))
```

## Make dataframe for annotating in the sample sizes

```{r}
datadeadsum <- summarySE(datadead, 
                         measurevar = "mass.max", #doesn't matter, just need the Ns, will be NAs anyways
                         groupvars = c("treatment", "food"))

samplesize <- data.frame(N = datadeadsum$N, 
                         treatment = datadeadsum$treatment,
                         food = datadeadsum$food, 
                         x = c(1, 1, 2, 2, 3, 3, 4, 4), 
                         y = 1.05,
                         fate = NA)
```

@@

```{r}
barsdead <- ggplot(data = datadead, aes(x = treatment, fill = fate)) + 
  theme_bw() + 
  geom_bar(position = "fill") + 
  facet_wrap(~food) + 
  scale_y_continuous(breaks = c(0, .25, .5, .75, 1), limits = c(0, 1.07)) + 
  labs(x = "Treatment group", y = "Proportion of indiviudals", fill = "Developmental Outcome") + 
  scale_fill_manual(values = c("purple", "#1E88E5", "lime green", "orange", "#D81B60"),
                    labels = c("Died", "Wander", "WE", "Small WOWE", "Large WOWE")) + 
  geom_text(data = samplesize, aes(x = x, y = y, label = N))
